# Performance analysis of the Parallel quick sort algorithm

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(plyr)
```

## Basis analysis
This software is composed of three algorithms:

* A sequential sort algorithm
* The libc sequential sort algorithm
* The parallel version

```{r echo=TRUE, message=FALSE}
dfw <- read.csv("data/amoweb_2014-11-14/measurements_20:58_wide.txt",header=T)
dfw4 <- dfw[dfw$Threads<4,]
dfwHigh <- dfw[dfw$Size>1000000,]
dfwHigh4 <- dfwHigh[dfwHigh$Threads<4,]
dfwBig <- read.csv("data/amoweb_2014-11-16/measurements_20:19_wide.txt",header=T)
dfwBig4 <- dfwBig[dfwBig$Threads<4,]
```

The test is done on a Intel(R) Core(TM) i7-3632QM CPU @ 2.20GHz (quad-core hyperthreaded).
 
We execute several time the program computing with each of the tree versions. Each execution have several dimensions:

* The number of Thread (from 0 for no parallelism, to 3 for quad-thread execution).
* The size of the array
* The execution time (for sequential, LibC sequential and parallel versions)

The machine is a quad-core hyperthread.

```{r, echo=FALSE}
#names(dfw)
#plot(dfw[names(dfw) %in% c("Par", "Threads","Size")])

```

The first figure shows the execution time for several threads. It shows for a little array, multi-thread is counter-productive. We use a logarithmic scale to show these little values.


```{r}
ggplot(data = dfw4, aes(x=factor(Threads), y=Par)) + scale_y_continuous(trans="log2") +
geom_boxplot() + facet_wrap(~Size);
```

The same figure, with a linear scale shows the threads are useful for big array. 

```{r}
ggplot(data = dfwHigh4, aes(x=factor(Threads), y=Par)) +
geom_boxplot() + facet_wrap(~Size);
```

Now, we display, for a size of 10e8, the duration for each number of thread. We see the average computation duration is decreasing.

```{r}
ggplot(data = dfwBig4, aes(x=factor(Threads), y=Par)) + geom_boxplot();
```


## Micro-analysis

We use GNU Prof to evaluate the time performance of each part of the parallel version of the quick sort.

We can see that most of the time is spent in the partition and swap functions. It seems to be coherent since these parts are fully sequential.

<pre>%   cumulative   self              self     total<br/>
 time   seconds   seconds    calls  ms/call  ms/call  name<br/>
 55.97      3.35     3.35  4474951     0.00     0.00  partition
 40.93      5.80     2.45 109078628     0.00     0.00  swap
  1.34      5.88     0.08        6    13.34   980.80  quicksortHelper
  1.17      5.95     0.07                             main
  0.67      5.99     0.04        1    40.03    40.03  isSorted
  0.00      5.99     0.00        1     0.00     0.00  parallelQuicksort</pre>

An analysis with Callgrind (Valgrind) show that we spend a lot of time in the swap and rand function.

<p><img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAA0MAAAGMCAIAAACXg+7wAAAAAXNSR0IArs4c6QAAAAlwSFlzAAAL
EwAACxMBAJqcGAAAAAd0SU1FB94MDwwRMAVpwHAAAAAZdEVYdENvbW1lbnQAQ3JlYXRlZCB3aXRo
IEdJTVBXgQ4XAAAgAElEQVR42u3dd3wUdf7H8c/M9iS76b2HhBQ6iBQFFFQUsZy9K9bDO8+GZz1/
1xCwn6eid/bezpNTsSKKBVQk9ARCCC2k957s7vz+WAiREhJI2dm8nvrYRzK7M7vzndnMm8935jtK
Y2PDrp273G6XeBODwRATG/v9d9+npCSLyNatBcdPOt4LP6evfv7eWP3KigqXa0Cs/kEZjcag4OAB
u0sc5V5kNBppEAA4+PFFRCwWc2tra1tbm1f9EReRlpaWpqYmzw8iIqK53W69HIR0/fl7dvUD7HYR
sTsCqyorBuw3TdM0T1P4+ftXlJcPtF3iKPcikhwAHIpSU1NdVFQUER4RFBTkOd4oisIjjz31KCK1
tbWeva26umogf9mCgoJFxBEYKJrGjnEEOxKNwCOPPPK436OIKNu2FcTFxdfV1tbX1xFs0RsGcqfq
oUpNAAD0TE2uoqLCYFCrq6poCwAAAH1Rg4KCGhsaaAgAAADdMba0NDudTs8vSckptAgAAIAubCvY
uv8VYdon79EuAAAA3mzW3+a/9MNK8YxCsp+vvviSBgIAAPB+Bx+laeqcLTQNAAADyqybf1z5zuO0
g3fKnfXMj1f9JCJ/vG/WPcdaD5PkROSrZRtpNQAABppty7JpBK/1yeKv9pvS2cjp/w0tpMkAAOgv
H8ydFbR0Uh+8Ue6sZz47dd9B36aafSH0jHjEN3aDOdfNWnljwKGePcw9cLJXLOOLBABAP+qXIplF
9YW75H34xVc+v3scfjtZTCrfIgAA+lhL2777Mgca/bo416JhC7r1Lp3Ue4yKL9yTprWxUdef3+zn
d7RJTkTMBsIcAAB9mD9c7v2mWLtcJOvBQpRBUdp/dpbXVz71VdPqnaJp1qGxob+faowK1EVjOtva
dLobGE2mw7+mq9tSVfheAQDQB1xu7eDH7C4XyZrqunQvdZvd3oUwt6eas/v+RX5jk0KvOl4UpX7Z
5uK7/pP48rW6aVKXU3e7gcHQpZDWjV5wwhwAAP0V4zxUpavHYmdr62ESgPnwlzWUPfRpxOypBrtN
RJxF1aGXTVTMRhExXxxS/eYKRfQUDDT3vjJnfXXVd++/UbglR3Nr0YMGTzrnUkdomFd9WkXtando
985n7PoOBAAAusutaYc/xnd9aW7XIQ/oapfKe6booO1XPR92zeTAGcMdJw/ZfvULARMGiaI0rMi3
n5ipu0yg7W3eT55/Ij596NjTzlIUJX/NLx8+88gl9zzgRTGuO3HL2P2l80UDAKA3ckZfLbTLx/Kg
y8YHnjK09LHPa/6XHfXHGX5jkppW79A0Lez6KfZJ6fpq3q/eeH7iWRdZbDYRqS0vG/P7mZ6z0EZP
PW3Vlx/3TusfYY7r1suNvf8WAACgh2Ncn+UOY6Qjdv75jcu37LrnPftxaeHXTVFtuhxtzhEa/sYD
d48//dzM8ZMGHzPhrQV/ShoyQlGU7RvXpo06Vr97zhGOFqOvrnEAALw6xh1ZMOv6TO01mO5Xnlw1
Tc6iGuvQuJRXr6946butl/0r4ndTHVOzdNfIx0w/c/DYid+8/fL675dOvfjquMFDdm/J1TRt/Mzz
UoaP8ZYdoc+SHAAA0FEEVI4oJtR+kF3xzyXGcLuzoj76rpnh158QOGN48cOfVi3KjrrjNHNciL6a
yx4cOvOGW7dtWP3xvx9PHjZ6/MxzTRar92zLI8NAcQAA6DrM/er/nlX5/LeJb9yQ/PaNSS9cU/bs
UhExx4XEP35J8Nmjd978hu7aqrmhvnRHQXTK4EvumW80W17/+91bVv2oiPT7/0eDmhwAAHoPc712
1pymKSaDiCgWU8eeWfuJmf7jU/XVSuu+XbLsvdf8A4Maa2umXXLthDPOyxp//NK3Xlr3/dKpF80K
iojqv+13VJuPJAcAgP7DXO9cehl8+YRtFy40x4e07aqKuPmUjk+pNpNoemqi5R++e9n9DzqCQ6tK
ihY9/dDgsROCwqN+84e781b9+N9/zp/1t8d1uumNhw2DpXdu5hsCAEBfyp31zLhBD3drFncvBKvA
C491nJjVVlhtSQg1hdv13aaaGIxGETGazR2Db9rocclDRyn9MTBHj+TvLtXkti3L5ksFAICXc/VC
Zc4Y6TBFBiqdBSR9lOaOOfXMV/7v9qCIqOrS4snnXd7xKZPFIv0wKEfPtFtXe1dtqplvCAAAfaDJ
3Uoj9LjR02akjjq2prQ4ODLGPzD4wBf0ZVmuB3vDjV3PhBaVk+oAAOhdLW4njdBL7MGh9qDORk7p
mzDXsyc1di+cGRVDj69P9fPftuQURz58/oFPFf/uddtxqYGXjGPnAwAMBE7Npd8Pr/nEJlDU3g1z
mruH26nbZTbDUcfVwhteCZiaEXjhnjtjWAdHGe1Wg6JoLvfW4+fHvXKNJS3S85T/+EHmQREG7g4G
AANP/oQeu6P5oOX3eH7Ydvo/XJUNHZ+KWnCe/+TBItL449aKJ5a07aw0JYSG3XKS7ZikA5fjqm4s
f/TzxuX54nL7TRgUNme6Idi/PcVUv7Gi9r+rnMW1hgh76I0nBpy0/10QmrJ3lM392N3Q4n9iRvgd
p3rOy2resLtsweK4F69WDKpL89Is5K5vUa0mz3Ake1a3zdVWUmOODfHRva/3gkcvnMh4BPMYlCMc
T1hrcykmgyKKImr7QhxTMvY8q4iIGDo8FXrlcfwtA4ABa/bs7h32Fi68W9Pm7X9MVpT2w0r8k5dp
Trfn5/plm6peXx5wbIqqqK07K4vveDf06kn2k7NqF68rmvNO0tuzTVGB+y1q9z3/1Vra4p64VLWa
yp/9uuSe/8Y/c4XnqfKnl9R9sTH0tyeYE8NcVQ2qzXTgsbJ83uKI26f7jU3ecc0LTd9vCZg0WNxa
+UOfRt5xmtFodGluL9wErqqG3Xe/37Rmp2ozBV9wbMR1J3jyXEtBWcHl/8pccf/BoopP1OZ6o4rU
O0m920lu16wX/I9NadlU3FJQrpgMETefHDA5XUSa1u0qe2pJy6Yiza35jUqMvHOGKTpIROq/yyv+
26LwG6dWvPS9q7ohYHJG09qdTWt3lj3+uTHEf9Di28qf+6Y5pyjukYu2nv1PEdl+xb9FxH7SkJi/
n7Nz9iv+x6eFXDpBRFp3VpY+9Enj6h2qn9lx2rDw352kGFUR2X7Vc/7Hp7XklTRl71Bspohbp9tP
yODPHwD4hoULa3qiwLLnqGxJiWifWPbPL+1Tsww2i4jU/neVJTUidNYkEQm7/oT6bzbVfpAd9tsT
Oy7EWdnQlL09YeGVtqxYEYm88/T8GY+25BRbM6PbimsqX1+R9NK1lsFRndRiWndW+o1KUk1G25DY
tp1ViihV/1lpTYvyG57gtemn/LEvneX1sQsu0Jpay59f1pxTFP/QhYrVNBD2vZ7Ncr1Xbz2Smlz1
eyvjn7zclhXTsHzLrjvfTX71enNiqLQ4Qy441poZ7W5srXjpu933/ifphWtERBFx1TU3/rI9+Y0b
RBTVZmorqrZPzQy5aNzeL9ie/wd98IdNx81NeuU6a4dvgucprdW56+bXrYOjkl+73llev/vPHygi
7UMUVr+3Mu6Ri2wLLqj9bF3xXxYFHJui+nGlLQAMNPMPneT211ZS2/jLtoQnL/c81bS+0G9kQvvL
/EYlNG8o3H+uVqeIqBajZ7rBYhSR5vW7bJnRjT9sMceFNKzIL7zjbc2l2aekh990krpf3FHEnBTW
+GO+/7hBTWt32Senuyrqq95c4TlWeq3G5flR984MmJKuiNinZOy6850dN78e/9glhw8uethj3n9i
3kmXXecIDe/sXwE9FOR6by2OJMnZp2VZs2JEJGBimv+YpJqPVkf8/iT/scntL4i+98xNJ8xzVdQb
w+yKIuLWIm85xeBn2fePI0XpcHmIIp6rRZQ9P+x7Stnze/3yfFdVQ8z/na36mS2JYZG/P6lo3ocR
N52sGFQRCTxtuN/QOBEJPHV4ycOftmwq8hudxJ80ABhoDuxa3Vtc2f94XLt4rSkq0H90kudI7apq
MAYHtL/MGBLQuHrnfnOZo4PM8SEVr3wfc/9ZitlY/vwyEXFV1CuK0lZc01Zc3fDDltj5F7jrm4vm
fuhubou5/6z93jTmvjOLF3xc+thnjpOHBkxM2/1//w294rjGVdvLnlmqmNSwO041DY/zuiZtaTPu
HRBY9TMnPHLxzjvf2XHTaxG/m9aV7eFV67Lp5x+0jn2/iuzIWZf3y48BwSGKoqSPPa6LO0/3d8ve
bYcjSXLmlH3p1TIoorWgXBFxltUVP/Jpw8oCV12z5ylXRYMpzC4iaoDFFBrQMd92vF+s8uvQu9+t
ZD2/thaUWVIiDHsrbX7D4txNbc6iGnNcsIiYY4LaZ1H9Le76Fi6RAAB0Ulep+Xh10IwR+x2jlQ4H
74Pe1zxu3vmFf3p/00kPKqrimJplSQoTVVFExK1pra6Y+840x4eISMSN03b/5YOYO09XLL86yPoN
i0t57QbPzw2rtrXurIy87dT8c/+Z+NK1baW1RX9eFPefG72t6cxJYc2bi21D90RMxWyIX3DBzjvf
KfzTf7oUYrxpXRY/94TBaNovY32/6C3Ppj5UkvN+RzREnGvfWZmac8/10oV/XaTazCmvXm+KDBSR
jRP/prn3vMxTOevN76jizf8IAAB4lcbs7a2FVUGnj9h3LAzxd1Xtu6bVWVFvCPE/cEZrWuSgt2Y7
K+oVk0G1mXOnLTBHB4mIMTRAFPHEOBExJ4RoLrezquHAayb2HjrdxQ9/Gvt/ZzVvKjInhJpig42x
QVqL01lcI1EBXtVW/tMy6z5dH3zOMfsOuWZD3IMX7Lrr3frvunQzT+85BTD9mAkNtTWnXH6DIyzc
c/LkP2689NJ754XGxB++8HZklbk+CSRHkuSaNhR2/NlvZIIm0pyzO+Zv5xijgzSRlvxSz4bTDprK
VVXrUGrU2h8VxbPW2q/jvCZiTg5vefk7V1ObajOJSOO6XarNbIwOPOjyNV8Z0gYA0CP2OyhUf7TG
b1SiMSaofbp1aFzDqu3tvzZkb7dPTj/UocQQGiAiNZ+s09pc/hNSNRHbsDjRpGVXlaenqHVXlWJU
DcH+h1pCxRvL/UclWtOj61fk7yv9qSJur7t8NfjKiWFXHb9/qjEZ4h++SGvT2QjGM667Ofen7999
9K9jTz1r+OSTuzu7cnR7nXclucafC2r+lx0wIbX203XNObtj7jtTRMwJofXf5wWMT3U3tZb+88tO
ZjdFOprW7nKeUq+YDAaHrUPCU4zh9saVBaYIh2IxdrxqIWBimiHYv+hvi8JnT3WW1ZU++WXQb0b3
eqkPAND/5vfs4txNbbVLNkbNOe1XeeXs0VXv/lT+4reOk4fWLF7Tuqsy6KxRnqd2//kD29DY4PPG
ikjd0hzNrZmig5pzdpc+tSTsiuM855DZhsbZhsUVz/so8rbp7vqWsme+Cjx1+H5dq+3aimuqPliV
8vJ1ImJNj24pKHeW17WV1oqIMTrIKW59bBZFFLOx62nFSypz6WMnxqamf/HKv7Zk/3zyFdd3f627
HOf6sHvwSJJc8CXj65dtLnn4U2NoQNzc8yxJYZpI1N0zi/7yQd6MRwzB/mFXT67/Mf9Qs4dcNnH3
/e/nzXzMGOSX9sntHZ+K+N1JpU9+WfLPLxwnDYn9+7n7ms5sSHjisuIHF2+95BnVzxx42vCI353E
nzcA8G0LF3avDqIoh499dUs2imj2aZkdJ5oTQuMfuqjk8c/Ln19mTgiNf+Riz0BaItK8qai9p9Xd
4ix7aomzot4YFRh+zeSQSya0x5q4BRcUP7h429XPKyaDfVpW5K3TD/UBSh77LPy6KQa7VUQMwX4R
N5+8fdbzikGNuHemqIoXdiq17apsLajwGxZnDPZvK66p/niN5nQFHJfWfvKc92WbzgQEhfzmpjvX
LPvyrfl/0nzidKwjGhnYbo19+EJl7zmhHta0yOTXbmjfBR3TsjwhPOC4wYM/u6PjrmlNjUx5Y3Z7
Sg+/dornBxEJPHVY4KnD2p9KfPrK9qfMcSEJT1y2X8IXkeSXrmv/WURSP7i5468AAJ066KizR6jD
QSHw9BGBnjPkfn2k8B83KOXN2QfOsueA5TlITR8WOH3YQZdsDAmIm3/Bod60Q9iUuAW/elnQmaMC
zxyliebS3F54j4eGrzcV3/u+59Af/8jFu+542xDsJyLlL34b+7dzHScN6dbS3F5yeFaUEVNOSRoy
omR7fkBwaPfnVjoNrH29jkb+WAAAgIOqfO7b4EvGR9w4reaj1TtvfzP47DERN07VRMqeXVr+4rfd
TXL9TnO7d27aUFywpbGuVhTxsztKtuXHpw9RDAb9bqNeSXIaNTEAADpQRJcDZLVtKw+cd56oStDM
kSULFjtO3hPdAk8fUfHK9/oKCbUVZR88+WBlcWFIZIxfYJBo2s66muUfvhcaHXf27//oCI3o9iY9
cM10keTiXrz6iO+7CgAA9BRAbWZXRZ0khDqrGzWX21lRL2mRIuKqbFBtR347pX7pRv7y1X8FhoWf
e8u9fnaHJ1orIo31dV+88uwXr/7r3Fvu63bjKP28Rh2SHBU0AABwAL+Jg4rnfhx4+vCG7/IcJ2WV
/ONzzTlNVKXs6a/8xw86umX3dfjYlZd76X3z/OyOX62g3THpnEten3uXfrdR754nR0QEAAxker/n
UNhtp1Q89Fntp+sDjkuNvOnkksc/33nH2+LW/EYnRd52qr5Cgi0goKq4KCQyZr/plcW7rf52khwA
APA1hkBb9Nxz2u+MHnXb9Igbp2pubc+Yr0edxfoyzI2aNuPTF58cPvnk2NR0mz1QFGmqqy3ckrv2
my8mnHE+Sa7z7URtDgAwsCjim/cAV62mnj6o91FIOOaUM/zsjuyvPl21ZLHnhqKKqkbEJ0295Joh
E6aQ5AAAwEBRNPfD5s3Fe4Z01UuUE8kcPzlz3CSXs625oUFEbAEBBpNZ79vC2GctSF0OADAQKANg
HS0p4YpZr8Ugg9HkHxjsM1XTvt0MGnEOAODbOW4gBDkJuXi8SA8XaTRCgg6SHJU5AIAPpziaQIe+
eOXZsl3bL713vk4/fz+URrkAAgDgizHO94Nc85YSZ2mtIdxhTYvstZDQ10Jj4o1mHZ8txxUPAADg
4MoWfBJ29SRTRKCrpqnwj+80rtnhme43MiHu4YsMAVYfiHOjT5qh6LlPvN+SHJU5AIBv8OFqXO0H
2cHnHGOKCCz9x+dtJTXJL1xjTY9u2lRUeM97pU9+GX3XzF4LCT0vf83K+PQhJrPFx7ZRf9bkOLUR
AKD7GDcwTo6r/y4v6o7TbENiRcQ2JDbid9NKHvtMei3J9Yb/Pf2wyWJJGzUua8LkuLQsn9ly/dy7
6qYyBwDQLXXAXOTgbmo1x4e0/2qOD3FWN/b2m/Z4RBhz8szdWzb95/G59tDwrPGTssZPDgyP1Pum
4Tw5AABwSOXPLDXYbYrJ0FZcY8vcc9PStrI6Y5Bfn7x/T8a5QSPGjj/93LrK8o0rvt24YtmKj9+P
S8vMmjAl/ZjxJouNJHc0W4nKHABAT5SBUY0LvHCsp+4YeMbIjtPrv8/zG5nYZymhZ9lDwsbNOGfc
6efszsvZsPybpW+9uPStF27656skuaPbTGQ5AIBeYtyAGTgu7JaTDYqqiKKIdLzAM/rumb2Rsfoq
y+0Rm5YZOzjrxIuuzlu1Qr/byKt6V0lzAAAdBDmawN3U2pyz229Uko4+s58jUDUYDpxusliGTDyB
JEeUAwAQ4gaK1p2V22e/krni/r4NCUcVE2546FlN03yvE9DrrnggzAEAiHFewllapymKp3e1vXtV
E3FVNbA/eFWS87b4RJwDABDk+t/2s/7JhtdFkvM6RDkAACGu36kB1tBrJvmNTFR+fZ1H647Kwvvf
11dIeOyGizp59rZ/vUOSAwAAPsWSEaU1t1kzoz3Xrrb3ropB1ePqaIc4SY77rvZ1iwMA0DcUZUBf
5BB44VilxXXgdFN0UOzfz+33mMD+KdTkAADAofgfn2ZQDlJ+M9itjpOH9HuUIsrpI8mxnQAAfY8B
R0CSI84BAAhyICP0cpLT9LDDEuUAAIS4PpY/4YFOnu3jkYEJCYdMcgAAAAcPSbq53nOAxjmdJTkq
cwCA3kM1DiQ54hwAgCAHkOTIcgAAUhzICD6Y5MhyAABSHCCi0gQAAAA6pe9rVzVqcwCAo6BQj4PO
UZMDAAAgyQEAAKBv+cjIwHSyAgC6ji5V+AxqcgAAAHplFBHRNFF8498n1OYAAJ2jHgffS3I+hCgH
ACDEYeCgdxUAAECvjL65WpTmAAAdUY4DSY4sBwAgxUHHe4Jy96+igjbvwIkkOeIcAIAgB280e/a8
9p8XLrxb7xluICQ5AACA9vTmg7GeJAcAAHzfrc++pWmaaJ7+OmXPPXcVz4OOE96ASHJ0sgLAQEOX
ao+15AFdkJ7Ty0CSAwAA3m727HkLF9Z0mDDfN04v8xmMJwcAALruLpG7aAXvQU0OAAB0ZvbswAOm
zVu4cD4tQ5LrBxpnzQGAj1I4O64X+OT1niQ5AADg+wYtv8egqIooioiy9wrPfRURaiNegPPkAAAA
SHIAAAAgyQEAAKArBvp5cnTxA4B+cSo+oIrI3jtXAAAAQHdJDgAAADrEKCR7UZgEAL1Q6FYF9qAm
BwAAoFfU5H6FuhwAeDNqccB+qMkBAACQ5AAAAECSAwAAAEkOAACAJAcAAACSHAAAAHoKo5AcHkOT
AEDfY8ARoCuoyQEAAOiVUUQ0/unTJdTmAKBvcFACuoqaHAAAAEkOAAAAJDkAAACQ5AAAAEhyAAAA
8D5GERGNqzKPBK0GAEeP61SBo0FNDgAAgCQHAAAAkhwAAABIcgAAACQ5AAAAkOQAAABAkgMAACDJ
AQAAgCQHAAAAkhwAAAAOz0gT9B6NG3oBGPAUbscF9CZqcgAAACQ5AAAAkOQAAABAkgMAAPD1JMdp
+QAAAHpNcgAAACDJAQAAoO8YRUQ0+lf7Fu0NwPcwbBzQH6jJAQAAkOQAAABAkgMAAABJDgAAgCQH
AAAAkhwAAABIcgAAACQ5AAAA6JORJvAqjBkMwJsx+i/gbajJAQAAkOQAAABAkgMAAABJDgAAgCQH
AAAAkhwAAABIcgAAACQ5AAAAkOQAAABAkgMAAABJDgAAgCQHAAAAkhwAAABIcgAAACQ5AAAAkOQA
AABAkgMAAABJDgAAwFcZaQJfodEEALpMoQkA30BNDgAAgCQHAAAAkhwAAABIcgAAACQ5AAAAkOQA
AABAkgMAACDJAQAAgCQHAAAAkhwAAABIcgAAACQ5AAAAkOQAAABAkgMAACDJAQAAgCQHAACAvmOk
CQYsjSYAfIJCEwADGDU5AAAAkhwAAABIcgAAACDJAQAAkOQAAABAkgMAAABJDgAAgCQHAAAAkhwA
AABIcgAAACDJAQAAkOQAAABAkgMAAABJDgAAgCQHAAAAkhwAAABIcgAAACDJAQAAkOQAAABAkgMA
AABJDgAAgCQHAAAA/TF28XWfjHiExgIA6Nec62Y539ri/Z9z1axV6qyr2V7o4SQnIh9+8RXtBQDQ
tbxleTQCBmiSE5G2lhaaDACgOyaLpf3nEyeP9c4PuWTWd+osCxsLvZjkRMTV1karAQB0xGAy7Tdl
47IcmgUDNMmJiNvlpOEAALqgGg5+pAsw2ru7qHMmXtZLH/K5Wc+ZZ1EoQV8lORFxu9y0HQDoyyPX
nd9Ti7r93+96fvjli4/WLvuyprxEVQ3RKWlTLrgyIj5JRCqLd3/33zeKC7bUVVXMuOamzPGTD7Wo
yqLCr999ZdfmDSISlZx2/m33K4oiItVlJV+8+uzuLbm2AMcx088cPW3GgfPu2rzxs5eebmluGjx6
/EmXXiuKIiJFBXlfvPqvy+6br6oG1dDZEA0Wtdtdmd9+9S07EnwhyYmIphHmAEBnZs/WDpy4cOHd
mjav6wtRFKX9EGD195945vmOsIiWxoaVn3/43qN/vW7B00aT2dnaHBgWkT524qcvPKVp2qEOGXWV
FW8u+NPgMeN+84e7DQZj2c5tmuYWUdwu1/v/mBsWG3/ZnxaUF+789IUn/QODBo8Zv9/sn7/8zIkX
zUrIHPrGvPu2rPl50IhjNLf7y9f+Pe3iqz1x8PBHQcXQ3TZsq+/h4pkpwMSeib5Ocjkrlv3w4bs1
5aUWm19i1vAZ1/7h67dfam1uPuXK34rI5y8vzFnx3Y2Pv2CyWHbnb37/H3NvfPwFVTV8/fZL+WtW
1ldV+QcFjznp9FHTThORtpbmJ/9w1dRLrln/7ZL66srA8MhTrpwdEhXDtgGA3rBwYc3RL0TT9iTC
jsU2/6DgV/48p7aiPDgyOiwucVJcooh89tLTmmjtr9/P8o/ei03LmHbptZ5fo5JTPQsvWL+6prz0
orv+bvXzD46M2bV546ovF6eNHrffh6gqLYpNy1QNxujk1KqSIk3TVn/9WXhcYvSgwV1fF1X2hbmW
8tbNTxZUra7RNAka6hh8U7It6iB1O1erq6c2h8FsYJ9EXye5hprqT198+pSrfhufPrSlqaFoa56m
aTGpGd//9y3Pd3VXXq7ZZivaujk+Y2hhXk5UcpqiqJqm+QcGz7zhNmuAvWRb/pev/TsoIipp6EjP
LGu/+fycW+7zC7D/8L93Fj354BV/flg1sHMDQB+YfzRJbl8Gamrc8P3S4MhoR2j4/s9qcqgkt3Xt
L8Mnn/zeo38r27U9MDzyuLMuTMgcJiJFW/PCYuItNj/PjLFpmeu+/crtdu9XaQuJit22cU1i5vDC
LZtSho+pr6n65cvFF9/5t+6uTvti196fG3pMcMqsBEVRSpeVr75z48RXRh+8BVza0Te9YlDY/9AP
Sa6pvlZEUoaNsvgF+AcGhUTGiKbFDkqvLituqK4S0Zrr64Ycd8KuvJz49CGFebmxqemiaSJyzCln
eOobBvEAACAASURBVJbgCA4tLtiyZfXPSUNGeJ4ac/JMvwC7iIybcc7qpZ/tyFmbNGQkmwcA+kC3
ulbb5+mYxj589jHN7Q4Mi/jNH+5WVVX2z22aHCzJOdvaGmtrfvniw0nnXHrChVdu+OHrRU89dNl9
84Mjoxvramx2R/tcfnaHy9nW2thg8fPvuISTL7/+qzdf+ObtlwcfMyFpyIhPX3xq7Cln7MrL+WHR
2waj8aTLro9Pzzrsqmx8cMvgG5ONdoOINO1uTro8VjWrIpJ4cWzBG4WaHDqxdegxbqlq2fzm5urc
ak3TgtKC0i5Js4XZDvPG3GUJ/ZXkQmPiY1LTX7j35uRhoxMyh6aNOtZotvg5AoMiogq35IqmxQxK
j0vLzF7yiaZpu/M3jT5pz2mq679fuurLxdWlxW63S0RSho/puEzPDwajMTgypqKokCQHALoQN3jI
ZffOa6ytyV766aKnHrz4rrlmq7VrcdAtIoOGHzN88kkiMvncywrWZeesWDbxrAv3e6EiB69dRaek
XXrvnhi6a/PG6tLiEy648sX7b7n03vn11ZWLn3vihgcXHvZT2KKty69cNejaxJjTIqJODl8xa3XY
hGBRlIoVVVEnhkrnpbe9n2vtk2tDh4amnJ0iipT9UrbmsTXjHxjf6bqz46BnHMm/CBRFuWDOn2fe
cGtAUPCPH//39Qfu8YwYHJuaUZiXW7glNzYtI2ZQevH2/LKd29paW6KTU0WkaOvmpW+9dPxvLpr9
6L9vWfjG+NPP1dzuDl/nfeccMMoJAOiI2WoNjYmPzxh6+nW31FdXFazP7motwWwxW61BkVHtU4LC
o+prqkTEz+5oqqttn95QW20wmsw2v0Mtyu1yLX375akXX126oyA4MiYwLCIuLdPZ2lpTUXbYj5F8
edyxC0eUflP+02/XRp8akfb7JDEoItqg6xIy7hikidb+/34z5ryQ42zcc8BqLmtOOiPJP9bfP8Y/
cUZic2UzOwa8N8l5wlxC5rDjz7nk0vvm1ZSVFhfk7UlyW3ILt+TGpmZY/QMcIeGrliyOSEg2mi0i
Urxta3h8YsrwMSaLVUTKd+/ouMDignzPDy1NjVUlu0OjY9k2AKAvmubu+E/0rohOHlxdWtL+a015
SUBQiIhEJ6eV797Z0tjgmb4rLycyMbmTy1FXLVkcl5YZkZCsaVp7AU9RlS5+HmukZeSCrJQr49fc
k1P5c3XKlXFpNyaFTwrpfC5buG353ct3L9stikRNjPrxvh/z3szLeytvxX0rIsdFiiIH/x/o9yRX
vC3/ly8+qiwqrK+u2vzLCk00R1iEiMSmppfv3llTXhqZmCIisWkZm1Yuj03N8MwVHBlVWVRYU14q
IgXrs7etX91xmdlffbIrL6e2vOzL1/7tHxickDGMbQMAvWP+r/8/KkvfeqlgfXbpjoJtG1Z/uPBR
o9mcmDlMRNxuV9mu7WW7tmturbayomzX9obaas8sn720cM03n3t+HjXttLxVKzauWFZTVvLDordr
yssyx00SkcSs4YFhEV+89q/K4t15q37c8P3SkSeeeqjPUFdZvu7bJRPPukBEIhKSKop21VdXFW/L
F5HAsIiurEVbTVttbn3QUPuEV0cZrIbll2cXf1XesRp30Jpc0hlJY+8fW7qy9Oc//xwzOWbwpYMV
gyKKpJ6fmnVNlnIw7HzocUdynpzZYt269pflH77b2tIcHBF92qzfeb4qgeGR/o7AkMgYz2WnManp
a5d9GZuavmePHzJy2KRpb86/z2Lzi0hIHj7l5KriovZljp953jfvvFJZXBgen3TWjXdw4SoA9IaF
Cw8SJhTlyPNca3PTktefb6itNlttsanp599+v9U/QESa6uten3u35zU/LHr7h0Vvjz/93PEzzxWR
0h0FfnbH3kPDiGmXXPvjx+/XVVWERMWedeOc4MhoEVENhrN+98clrz/3+ty7bQH2486+6MDB5Np9
8+6r42eea7H5iYgtwDH5vMvfnHevajBMv+pGRT18wWLXB8WbnthqCTe3VLRl3ZU66LqEqNPCcx/O
L1xUnD4nxS+us3P+rKHWkbeNLF9Tvvqx1eGjw1PPTzVYD3384tw4eEmSC4mOPf/2/9M0t6Zpmvar
K5Kum/+056+CiGQce3zGscd3nHHSuZdOOvfSA/+EiEh4fOKl981newBA77nlmTd7fJnTZ9140On+
gcGHervL/++hjr9mTZySNXHKgS8Liog699b7Dv8JNG3mDbd2nDD0+BOHTZqqKIqidKnfactz2497
c4w1ytKwvWnV7RuiTgrzi7OOeiyrZGl59q0bJ77b2eV3bfVtTWVNQWlBExdM3PrB1h/++MPgSwdH
TYg6yMd0k+PgNUkOAADfoYlqUkXEYFGlQ96KODEkeHyg+9CVtF1f7dr8+mZLsKWlumXIdUNSL0iN
PSE25/mcXUt2DbluiF+0HzEOJDkAAHpX8uVx316w0i/e2rirOf0PyR2fMthU96FvTZn/Xv6EByfY
wmyNxY2rHlwVdVyUX5TfMX86pnhF8c9//3nK01PakyKg1yTXlXM7zRbrrb1Q8AcA+LAeTEeJF8VG
TQ1vKGzyj7eZw0wHe69DvptqVEVENasdRwmOmhAVPjp8zyGQGAddJ7kuxzkAAPolyImIWCMtlkiz
aIcMbQednnRG0ve3f+8X5ddY0phxeUbHpwxWg6Ioh7pHGaCvJEeWAwB4bYrr+vvu/8aJpyVGjots
LGn0j/W3BlvZMvDdJAcAgC+yhlqtoVYKFuhH3L8XAABAr/q0Jsfw1gCAI8M5Z0D/JzkAALxQ466m
uoKGoKEOU5Cxqbhl98clbqc7dGKQfag/jQOS3IGozAEAuq53q3ElX5evuSdXRDPaTaMezlr9x43m
YJMmUvDSriF/TQ2bFswGAEnugChHlgMAdCXE9X6fav6/dyRdEpv2u6TCD0uy52yIOzsqdXaipmn5
/9q+7cXCzpOcu9XdXNFsi7QpRsXZ5CxfXa4oStioMJPdxLaDLyc5T5yj9QEAnQe5PniP+m2NI+dn
KaoSOzNq44ItUSeFe6ZHzwjf9uruTmasLaj9Zf4vbXVt/jH+o+8avWrequaqZnGLwWoY98A4e7yd
7QffTnKU5gAAnaS4PrrEweBnaClv9UuwtlW3ai6ttaJV0vxEpLWqzWAzdDLj5tc3O5Ic6Vek7/5m
98q5K+3x9uMeO05Efnngl82vbh5zzxi2IXw9yZHlAAD9meJERMInhqyfuznm9Iiy7yqjpoVteqIg
1Zkoimx5ZnvIuMBOZqzeUj1qzqiAuICU36Rs+2jbkOuHqEZVUZXkM5PXPL6GjYgBkeQ8cY7NAADo
GOT68s0yb0vZ+FB+0Wdl4RND0n6ftOkfW9f8MVdza8GjHWm3JnY2p1uMfkYRMfobFVWxBFk8k81B
Zmejk62IgZPkGGcOALA3xPX5uHGmQNPIuZnanruuahm3pqTOTtRcbtVPcYvm1tyHmtEWbmsqawoc
FCgiI28faQ3bc8Ou1upWayg378JASnKeNMfGAAByXN+/Z+myirBjg1XbvpseGayqpimauDufMW5a
nLt1z2sijolo72Eq+6UsZGgIGxMDLMnRyQoAAzzF9dP7Zv9xo8FmiJwaFnt6ZPAoR9ePRokzEg/6
4qzrszikYSAmOREqcwAwYHNcf96MK/nSuKq1NSt/v9YaZY2ZERE9I9wabenCR9Zk7wlCDYUNu7/d
3VLdYg21xp4Y6x/LzSEwMJMcAAB9LmJK6KDrEpqLWgoXl+z+uCT/+R3BIx3Rp4eHTQ1WrIcsMaz8
+8qoiVHxJ8VXrK3IfjDbFm7zi/Gr3lxdsKjgmPuOCRsZRsNigCY5LoAAgIFD69dqXEfWKEvK1fEp
V8dXZtfs/qhk0yPbNj1ScPySQw4LV7u1dvDFg0Uk7628xBmJgy8brKiKoiqb39ic82LOpH9MYuNi
gCY5AAD6UfAoR9BI++Dbk0q+Ku/8lW6XW0SaSppifhfTPjFuWlzBBwU0IwZ8kqMwBwC+zTuKceYQ
s2pUD5xusKlRp4d3MgpJcGZw0XdFwRnB9iR7dW51QHyAZ3rVxqr2EUmAAZzkRBTSHAD4bIrzlk7V
ExePUxTlCD5P+qXpP/3lp9aa1uDM4NxXcitzK/2j/RtLGou/Lx5641A2MfqGShMAAHAE/GP9J8yf
YLKbdn6x09XiKvq2aNuH21prWsfcMyZ2aiztg76hh/PkuAACAHyJ11zicPSsodYh1w8RRTSnpmma
0WZUVPqT0KeoyQEAcBA5D2xdOWt9V4+mJtVgMdBo6Hu6uXaVf+EAgN7pqxbnn2JTLBx8QJLryTTH
NwoA9JvjdNapmnBRtFu0Tq5dPZR1T62rK6g77tHj2OYgyQEA0Bec9U6DxdDxqOhu05pKmi2x5u4u
yh5vN5jpaQVJ7pCozAGAvnh1Na61qm31XTlVa2oMNkPC+dGDrktUTCIiDdsaf7pi3ZQfxnZ3gUln
JnGkAkmu0yjHNwQA9BLivL5PNfex/JbyllEPZjkbXfnP76jNqR/xUKZ6FGfIuZpdNfk1ocNC2fro
A1y7CgAY0MqWV6XflBIxJTTm1IjxL48URbJv2eBqdB3xAhuKGn6870caFn1D1+fJUZoDAG+mj0sc
3M0uS/iek+GMfoZRj2StvjNn1c0bB90Y3/mMzZXNew5Eyt7/VEVRldaaVrY9SHJkOQAgxfUF/2S/
2k31gUPtnl9VkzpiQcaaO3M33J/X+YzLfr+M7QySHAAA/SlqanjRZ6Xx50a3T1FN6vD5GWvvzm0p
r+rsCOpnHHTuoOCMYFFE8ZzBrYqiKg27G9Y8toaGBUmuqyjMAYD30N2tuFKuih80K0H79QdXTcqI
h9KdbZ2dLedIcbhaXI4Ux54kt7d3VTFwXAJJjjgHAAS5/j6wqGa1k5GBE09NdLUeJOrZImwjbx/J
rgCSHFkOAEhx3it8dPhBDz0mf1P0pGh2B5DkAADodZ+N/7aTZ49gZGCAJHc0KM0BQN/TdzlOO8T4
xQoj0YMkR5QDAEKcT/r8ks87eXbGohnsGyDJkeYAgBznxWtPMQ/9jbt1AQAA6JVvX/HAP4kAoPdo
NAHQ76jJAQAA6NUAGIWEwhwA9CyKcYDXoCYHAACgVwNlZGAKcwBw9CjGASQ54hwAEOQA9Ax6VwEA
AEhyAAAA6FvGgbjS9LICQNfRpwp4MWpyAAAAemUcwOtOaQ4AOkc5DvB21OQAAAD0yjjA15+6HAAc
iFocoBfU5AAAAEhyAAAA6FtGmmAP+lkBgF5VQG+oyQEAAOgVNbn9UJoDMDBRjjvgeKDcTSOAJAcA
gP5C2+zZ82gWkOQAANCF+b/+9a6FC4+8IEcxDyQ5AAD6yPQVkxRF0WTvfyKafKtpmiZut4xza+4u
hjbKeCDJAQCgL+3FvKMq4wEkOQAA+tQpb5yy5zI5RRQlWxRRVEVRFVFElNNoH5DkvILCxawAfI7G
haqAr2A8OQAAAL2iJtdFlOYA+AbKcYBPoSYHAABAkgMAAABJDgAAACQ5AAAAkhwAAABIcgAAAOgp
jELSRVy3DwAAvA41OQAAAL2iJncY3NMGAAB4LWpyAAAAJDkAAACQ5AAAAECSAwAAIMkBAADA+3Dt
6n64VBUAAOgGNTkAAAC9oia3F8U4AACgN9TkAAA4Qm6nu2BRgavFRVOAJAcAgN4Ooka14H8FBouB
pkB/Gei9q/SpAgCORtDgoKrcqpDMEJoCJDkAAHTGnmRf/dDqqIlR/jH+qlEVRUQREUmamUTjgCTX
q6jHAQCOVsWaClukrSa/pia/RkQURfFMJ8mBJAcAgLcb/8B4UURRFFFEURVFVdrLciKy/M7lE+ZP
oJVAkutRFOMAAH2iZksNjQCSHAAAQM+oLN69cfk3FUWFikhITNzQ404IiYrV7+owCgkAABgotqz+
+fW5d5cX7gyJjg2KiCzMy3nlL3fkr16p3zUaUDU5elUBABjQlr332pmzb0/MGiGKKCKiKD998sHX
77w8aORYkhwhDgAAeDW325WYNbzjlKwJk3/8+H39rhG9qwAAYKAIjYor2b6145SCddlJQ0bod40G
QE2OchwAoJ9MeWYKjeBVIhKS/vP43LQx40Nj4jSXq6hgy46cdWOnn7l66aee0QBHnzSDJAcAwEDh
bHRuXbS1amOVs8kp2r6R5KY8PUVEbOE2CgpeZXvOuqCIqLKd28p2bvOcJxccGb1l9c/tL+h6ktO8
Y8v6dpLj2wMA6F1rHl/TXNkcPy3eFGhSFMUzRHB7noO3ueTuuSIiorRf8SB77syh7Nl8essY1OQA
ADhyVTlV4/4+zpHsOOg9HtD3Blrb+2iSoxgHAOgOZ51z68s7K1fVOOudsq/jTBv71rDOZwyID2hr
bKMBdbOhW1uWf/Sf/DUrG2trNM3dPv2mf77a1YiheVfI8MEkR4oDAHTX6ntymktb486KNAebtD1H
a03rwiFlyA1DNr26ydXksifYFcO+mpxfpB+t6oW+fueVku1bp5x/xaKnHjz/tj+V7975yxcfjT31
LP2uke8lOYIcAKDbqrJrxj0/0j7YX0Q00TRN08TtFs3doWxz8KOOS2upasl+KHu/6TMWzaBV+1aX
ulXzsn86c/btsamZIhKXlhmXPiRpyMgvXnl2xJTpXYgY3pgxOE8OAAAJSPF31ruOYMZ1T69zpDhG
zRllCjQpKlc8eHGIExGRtpZmR2i4iBhN5ubGBmuAPSgiqqai7PApzlvX3YeSHMU4AMCRGnrf4NzH
tyY2xASk+Gmqp3fV7RbNHGXqfMamsqaRt4/0j/X37Sse3A0tLZuL3fUtHU8Ts0/O0FmOEwmJiqku
LbYHh4XHJ675+vMx088sWLfq8MU2zXtDhs8kOXIcAOAojiIuraW8NfuOjftNn/LDYW7HGT4qvCav
JiA2wIcbp27JxuK//08xGlR/S8fp3pLkumPU1NPqqipE5PjfXPy/px/+4cN3DUbT9Ktm63fr+EKS
I8QBAI7S2j9vcmQEjFyQYQ4y7T1PTnN34QjjSHZsfn1zdV51QHyAqqrtBbmkmUk+0zilj38eddfp
gacOV/Y77Pb3AfgISp9DJp7g+SE2LfP6BU9XlZXYQ8Js/ocM4prm7SmD8+QAAJDmouZRC7L8Eq3S
zSseSn4ssYZZa7fW1m6tlT1jzPpaktNanI7pw7zvcx1JH3bR1rzIxBTVYBQRo9kSHpfY+ap7/9bR
eZKjHAcA6Alhx4VUr6/1JLluGf/AeFHEc6GDr54nZxse37xxt21IrA+sy3/+8YBoWnRyWkxaRlxq
evSgwSbLwTe6ppOMoeskR44DAPQMR0bA5n8WVK+rDUjxE0U00UQ0t0jMueFdORxV51XXF9YrimJP
tAelB/lY41jSo3be9mbgjOHm6CDpcD+r4PPG9svnOZqcfOOjz5XuKCjcsqlwS+6arz9rbWoKT0iK
S82YcsGVusxx9K4CACAiJV+VW6Mstbn1tbn1e+OZJl1Ici1VLdkPZ9cW1FpDrSLSXNEcOChwzL1j
rCFWn2mchu/zTFGBjau2N8r2jtP7K8kdDdVgiEpOjUpOGzl1esm2/LXfLtn08w8l2/J/neT0VCrS
ZZLTKMYBAHrUhJdHibYnvXXrPLmcF3KMNuOUp6ZYw6yKqrRUtax9Yu2GZzeMuXuMzzRO4kvX7rnD
/H4xR4eH4+05awvzNhVuyS3ZvjUoPDI2LeO0a26KS8vct05una2VHpMcOQ4A0CuHl+r1dQ0FjZpo
/sk2x1D/rsxUsa5i3NxxnoKciFhDrVnXZv1w5w++1zhN63e1FpSJiDkl3DY0ru8/gtITpx/+94n5
Vv+AUVNPO+O3t9n8Azydxe3XqWg6rBXRuwoAgLSUt666fUPtpnprpEVEmktaHBkBwx4abAwxHCZe
GBRX869uDuFqcalG1Zcax1leVzjn7eZNRabIQBFpK6mxZcbEPXyRMUR/o+idcuVvC7fk5vz47S9f
fBQzaHBsWmbc4MyopFSD0aTps8tPV0mOXlUAQO/YuGCLMcA4edFYa4RFE625pGX9Xzdvfqgga15q
5zNGjotcv3B91tVZgemBqkGtyavZ8NyGqIlRvtQ4JQ9+ogZYUv93iznCISKtpbW7//xB8YOL4+Zf
0DcfoAcvBc4aPzlr/GQRpbGupjAvJ3/Nyh/+947BYPjDU6/pdOvoJskR4gAAvafip6rxL4yyRuy5
h4Elwpx+W/LP16477IwZV2RseG7Dyr+v9FR0FEWJnhSdeU2mLzVO409bE1+4xhTh8PxqinBEzTlt
29XP9dHb9/SQLvVVlYVbNhXm5xbm5VQUFQYEBcemZmq6rRbRuwoAgCgmdf9O0maX0oVOUoPVMPym
4W2z2hqLGkWRgLgAc6DZ1+67ajJozW0dJ7ibWhWjQY857oU/3VxbXhYSFROTmjF2+pmxaZmO0HBd
bxw9JDk6VQEAvSzqxLB1f92cOSclaJhDU7TqdbW5j2yNmBrSxdnNdrPZYd4zMrDPsZ+Yufuvi6Lu
OM1/WLwo0rh+V/FDn9inZeksxImIyORzL4tNTbcFBO67gELnMYOaHAAAknFbyoYH8n75w3rPqCOK
KpEnh6XecshbOVVurBT33qyh7Ln4UVEVz80eRJHQYaE+0zgRt55SMu/jHTe9Jp4ROlQl8JShkbdO
1+O6pI7cNwZea0tLcUGeIywiMCyCJNcrNM6OAwD0CYPNMPyvGRm3pTTsaNJE84u3GoMMnYwnl70g
u/1nt9OtuTRPQc7tdIsiBoth+tveFXSO5oCq2swxf/1N1O2ntm6vEBFzYqghyO9oF9qp3itsLn7+
n0lZI7ImTHG2tLw+967a8jJNtBnX/CFt9DiSnDftdAAAdJ8pyBQUZGofGbiTV057eZqnJle6snTb
x9syLs9wpDpUg9pY3Lj59c1ho8O87JDaA8dUQ5CfX5Bfnxyfe7GHevvGtRNmnieibV61QkRmP/rc
5l+Wr/jovbTRx5LkAADQmapVNYoYFGXvvR32pBRPktM00RyjDjNk2qZXN426Y5Q9we6JH/4x/iNu
G/H97d8nnJKg98apeeNH66AI+4TUyteXdxw/tz3JhV4yQU8hTkREWpubzFariOzIWZ86cqzJYknM
Gr7k9ef1u5m8MclpXOIAAOgT2bfntv/sbt3bSWoQd5smihis6vFLDnPTrZaqlv2LVJq0Vrd6yxoq
Rx6Nmr7foro0mZDa8F3eQUNWbyS53uYICduxaUPy0FEF67NnXn+LKEpLU5PJajmahiLJAQDQP6Yu
HaeKQVGUkm/Kt72+a/DNyY4Mu6haw/bGLc9sDxkfeNglhI0MW79wfebVmYGpgYqi1O+q3/za5pAh
Id6wdqp6VAOFRD11qUFRRCR+4RV9cN9VpfezlKIo42ee+/nLzyiixKSmx2cMVRRl+4Y1EQnJCkmu
Z1CNAwD0h9zHt45+KMt/0J7zwPwSbEP+kvbTVWsjzzjMGW9Dbhiy8d8bf7r/J000RVFEk8gJkcN+
P6z/D/Bmc08tKn/Go6mLb+s4xVXbtPXCp9MW366jTayoqogMOe7EpKEjm+rrQ2PiPOktPmNIysgx
nmdJckeX4vhDAgDoJy3lrQcchrTWSudhZzT5m0bcOqKtvq1hd4OiKl4yMrDNbu/BpTkrGw5oGpez
urHHMlbvN4jBsC/wOELCHSH7RgOOGZSu613Xa5Ic1TgAQP8Jnxi8/q+bM+akBGbZRZWGbU1bFm4L
GtWlPORsctbvrHc2OkWRqpwqz3hyUeP759arc66b1YNLq3n7J0VUEal868d9vaua1rR2lyW5p26N
0OtBzmgy+fCu6xVJjkscAAD9a8h9gzfMzfv5hrWa5jlhSws/ITT97uTDzliyomT9M+sVo2Ly+1Vc
6K8k53xrS7dev2rWKlWuPtSz9V/lem6FUPdVzr6bIqiqKdIR+9ff6CDEiZj9/Hx71/WGJEeMAwD0
M5PdOHJeZmt1a8P2Jk00v4TDjAzcLvfV3KzrsmImxYgie+7WpUj/9q7mLcvrqUXFPnuFQVGL/29R
zF/O7vErHnq7kXq2PEmSO0SII8UBALyDs8FVt7XRWe/UNK21uk0TtyYSMukwl6+6W93Rx0d727qc
OHnsYV+zZNZ36ixLV5YW/Zeze+Ez9nra7W550mt1Xjft1yRHjgMAeIfiJeXr/7ZZMSomf0PHg9O4
ScM7nzFocFDNlpqgtCBvW6ONy3KOcgm9NzJwn4340YPlSa/Vj0mOGAcA8BabHssfcldq1PRwEWm/
W1dXelcdyY7sB7NjJsfYwm0du1aTZib1+0pdMXn2Qac/N+s586y2w87eSyMDK33b99yV8qTX6krd
tH+SHMU4AIBXcbW4o6dHaN2vMpStKrOGWSs3Vu6JKXvLTd6Q5ETk26++PeJ5+3hk4N5z9OVJb9Yv
SY4cBwDwLkEjHDUb6xxZAd2dcfwD40URRVG854qH/bTW/urWYWZHt0cM7qmRgdX+axeHMVB3+2St
s8ZrkxwAAN7FMThg1W0bok+LsMVYREQTTURzi8ScG+4Da+du3dNHrJqP5E4GPTIycL/fDcuiWnS0
yVrcLV18ZZ8mOcaNAwB4p7LvK61Rlqrsmqrsvccs0cRXkpyIaG5NUbsdpnpqZGDFO6qUBsWgi43l
0lxdfzE1OQAAZMLLo0Tbk966dcWDq8WV/5/80pWlrdWtmltrTyzT357uA83S2yMD9z1V8fb7qx52
lyPJAQDQfYfoHcx9Obe2oDbjioxVC1Yd+5dj63fWFywqSDk3xTe6oWKfvUJ1ajuufjH+H5ca/MxH
cMWD4lXnDHo+tRdvGqX7ndB9kuToUwUA6DrFHTqOlP5UOvKOkSGZISISkhUSOiw0bHTY+qfWJ0xP
8JF1NxnaiqpUm+mI2s1raV66o3WfcaA2FgAA+7ia3fn/3l7yTUVrZeve3i1NRI5fMqbzqpKzfVLv
FQAABt9JREFU2WkLt4mIwWxoq28zB5r9o/ybSpp86ehnGxbfuHqH/6jEbsYSxZtXytu2zxE3lnFA
NRMAAAeV+2h+TU5d+i3J2bdvPObpoXVbGra/sTvh8ujDnlblH+PfWNxoC7PZk+w7PtuRfFZy6cpS
TdM0t+8cA63pUYV3vO04eYglMUwM+xok+LyxPZ5LesnZEy/RUYPPUeZkXJWR+1J++FWHv3cI58kB
ACAlX5WPeigraKRDRIJHBQaNcoSMD8x5YGv8OVGdz5g4I7G5vFlEBl86eNWCVXlv5akmdeiNQ30p
yTWsyDfFBjdt3N20cXfH6Z0kOS90NIMk97Gzlpy1aNqi4d8MKnqxgiQHAMDhOZtctmiriKgWta3W
aXQY/OP9motaPGNwHIrb6W6taU04LUFEgjOCT3jmhMbiRmuY1eRv8qVuqcSXru36PR4ULz47rrWu
VRcN/snZn2RclbF2Sm7/1eQYNw4AoCsBiX6NO5sskWbHYP+d/ylKuiy27Lsq0bTOryVUjWrB/wqS
z072XA6pmtWAhABh/FQv1j5IstdSzSo1OQAAuifx4tjmkhYRSbsxKfuOnPx/7VBN6tA/pR22whQ0
OKgqpyo4I5g2VHTyOTWXF49CYlBEZNG0Rf1dkwMAQD/cbVpLZWvi+TEiEjwqcMpHxzbubLJGWUz2
wx8l7Un21Q+vjpoQ5Rfj1/EmCj4zComIuJvbKp77pv6bTc7KBnHvq2mlL71bp2vknUXT9gIwNTkA
ALpBNSkFr+xKuSJ+z6HRanCkBXQtEUjFmgpbhK0mv6Ym/1f3O084xXeSXOmjn7XkFkXeOn3nbW8m
LryieUtp5evLQ684Ttcr5W3n82kdzjqkJgcAQPcEDbdXrakJHhnYnQAoIjJ+3njvWQtD7wzhVr80
J/ahCz3jyfmPSvIbnRQwIbVo7ofB5xwj3n2Jw2HTnPfkuI6oyQEA0D2OwfbsORujTg73T/RTDR06
Sc+POXgGMHhdfFF7LZi4m1pN0UEioliMrtomNdBmjg9pK6pmt+klfV6TUxQaHQCgX5qmla+otMVa
azbW1Wys6/hU/HnRB77eYDZ42yoovXksNieGte2sNEcFWgdHVb73c+jlE+u+2yxuTTj+944+rckp
xDgAgJ65xSUi414a3smzHZkCTN62Cl3p3+x4NUZ3BV80rq2kRkQifzdtx5y3yv71tWI2xPzpLHae
XtJ3NTliHABA15yaq+svfm7Wc164Cl05Eqtm9WjeIvCMkZ538RuVOPjj21p2VpqiAg12q+43v7eO
RtJHNTlFUfkTAADQrxZ3S7deH3JdL2aXemfbEcW4wwc5s8N89B+vdXt5zUdrWgvKRcScHBZ8xiij
zpOc5sV34eiLmpxqIMYBAHSs3lmn+3U4XIrrqSJi/de5u//0vv/YZEtKhOZ0NWbvqHxzRdy88+2T
0/Xact7dqdjrNTnVwBWvAAC9WjLrOx9Yi64kkfDr/Q/1VE1bN648Lf3HF3EPXRgwIbV9SsXL3xU/
9lmAPpOcF153vJ/erckZTCb+CgAA9Cvw2jCv/Wx1rp6sFHYrrnVCc7n9xw/qeF8Ex2nDy55fpsfb
yx7lKYN9oxdrciaLhT8BAABd69m01Pe6kp56tu5oSQ5ryimyZu4bkKX+hzz/8YN0lOPmKHPOWnLW
J2d/4glJ3v/Y8zW5OdfN4ssPANC1VbNW6X0V3F0rg6mzerLyYkmP2vn7V+3TMs3J4eJyN60vbPy5
IOSyCVXv/uR5QdD5Y7283TKuyvDEI708ikgP1+RW3hjAnwAAgK6pcrWuP39Xxkzp8bTq0twNP201
xQc3by5u3lzsmWiKD677Jrf9Nfbzxnh50+W+lDv8m0Frp+jpsYurpjQ2NhQVFhqMRhFJSk7RPnnv
qy++nDpny1fLNv43tDB7xbIf8+fw5QcAoI+NG/Tw9iUvBi2dtG1ZdqDRr/feqMbZ2Pzij5+dWvjq
f+pWvvP4tmXZNtVsUY1GxaDrBoyb8G3esjz3iy26Xgt1lqXuxTp11tXNL/7441U/fbL4q6U/vHrP
sdZXV6x86YeV2wq2GruyJ/F1AgCgH9U4G/v+Tbs1bLI3JyHf3jc6S3IfzOXcOAAA+lPurGf65X1b
3E69N50PnBZ5tEnu5d9+zlcIAICBpsnd6gNroc66eiBsrIMnuVk3/8h+DADAQNNfJUB0xR/vm9XV
JHdB9AW0FwAAAw2Hf682Wrqa5CxGbuQAAADg7fZPcrP+Np9GAQAA0GWSe+mHlTQKAACA/pLctoKt
tAgAAIBeqJs3b/Lz505cAAAA+mPcsG5DyJRQs9nS2NggIoqIxiOPPPLII4888sij1z+KyP8Dyxv1
pUz+qr0AAAAASUVORK5CYII=" alt="plot of chunk unnamed-chunk-6"/> </p>

## Conclusion

We could improve the performance of this parallel quicksort mostly by improving the partition and swap functions. For instance, we could make it parallel or use vectorization instructions as SIMD (AVX on Intel).
