# Performance analysis of the Parallel quick sort algorithm

## Basis analysis
This software is composed of three algorithms:

* A sequential sort algorithm
* The libc sequential sort algorithm
* The parallel version

We mesure several executions of each algorithm. We load the result in a matrix.

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(plyr)
```

```{r }
firstdf <- read.csv("data/sama_2014-10-13/measurements_03:47.csv",header=T)
dfw <- read.csv("data/amoweb_2014-11-14/measurements_20:58_wide.txt",header=T)
dfwHigh <- dfw[dfw$Size>1000000,]
dfwHigh4 <- dfwHigh[dfwHigh$Threads<5,]
```

The first plot shows, for each size, the execution time of each solution.

```{r}
plot(firstdf$Size,firstdf$Time,col=c("red","blue","green")[firstdf$Type],type="p")

```

```{r}
names(dfw)
plot(dfw[names(dfw) %in% c("Par", "Threads","Size")])

```

```{r}
ggplot(data = dfw, aes(x=Threads, y=Par)) + scale_y_continuous(trans="log2") +
geom_point() + facet_wrap(~Size);
```


```{r}
ggplot(data = dfw, aes(x=Threads, y=Par)) +
geom_point() + facet_wrap(~Size);
```


```{r}
ggplot(data = dfwHigh4, aes(x=Threads, y=Par)) +
geom_point() + facet_wrap(~Size);
```

A lot of perturbation ?