# Performance analysis of the Parallel quick sort algorithm

## Basis analysis
This software is composed of three algorithms:

* A sequential sort algorithm
* The libc sequential sort algorithm
* The parallel version

We mesure several executions of each algorithm. We load the result in a matrix.

```{r }
df <- read.csv("data/sama_2014-10-13/measurements_03:47.csv",header=T)
dfw <- read.csv("data/sama_2014-10-13/measurements_03:47_wide.csv",header=T)
```

The first plot shows, for each size, the execution time of each solution.

```{r}
plot(df$Size,df$Time,col=c("red","blue","green")[df$Type],type="p")

```

This plot is not easily readable. We would display the relative acceleration to the the LibC implementation. To do this, we can't work on several values for each size, we need to compute the average time of every method for each size.

```{r}
dfw_rel = dfw
dfw_rel$Seq = dfw$Seq / dfw$Libc
dfw_rel$Par = dfw$Par / dfw$Libc
dfw_rel$Libc = dfw$Libc / dfw$Libc
```

```{r}
plot(dfw_rel$Size, dfw_rel$Par, col="red",type="p")
plot(dfw_rel$Size, dfw_rel$Seq, col="blue",type="p")
```

